\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{amsmath}
\title{Midterm Report: GNNs for Molecular Property Prediction}
\author{Rahman \and Samarth \and Toral Chauhan}
\date{\today}
\begin{document}
\maketitle
\section*{1.\ Objective \& Scope (Short)}
We evaluate GCN/GIN/GAT on MoleculeNet datasets: Tox21 (multi-label toxicity), BBBP (binary blood-brain barrier penetration), and ESOL (regression of solubility). We use \textbf{scaffold-based splits} to assess generalization to unseen chemotypes.
\section*{2.\ Data \& Splits}
\begin{itemize}\setlength\itemsep{0.2em}
\item \textbf{Datasets}: Tox21 (12 tasks), BBBP (binary), ESOL (regression).
\item \textbf{Split}: scaffold; deterministic with fixed seed; no scaffold overlap across train/val/test.
\end{itemize}
\begin{center}
\begin{tabular}{lccc}
\toprule
Dataset & \#Mol & Split & Targets \\
\midrule
Tox21 & \textit{N\_tox21} & scaffold & 12 AUC tasks \\
BBBP  & \textit{N\_bbbp}  & scaffold & ROC-AUC \\
ESOL  & \textit{N\_esol}  & scaffold & RMSE/MAE \\
\bottomrule
\end{tabular}
\end{center}
\section*{3.\ Representation}
Atom: type, degree, valence, aromaticity, charge, hybridization, ring. Bond: type, conjugation, ring, stereo.
\section*{4.\ Methods}
\textbf{Models}: GCN (baseline), GIN, GAT. \textbf{Training}: Adam, lr=$10^{-3}$, batch=128, early stopping, seed control. \textbf{Heads}: multi-label (Tox21), binary (BBBP), regression (ESOL).
\section*{5.\ Results (Midterm Milestone)}
\begin{center}
\begin{tabular}{lccc}
\toprule
Model & Tox21 (AUC$\uparrow$) & BBBP (AUC$\uparrow$) & ESOL (RMSE$\downarrow$) \\
\midrule
GCN  &  &  &  \\
GIN  &  &  &  \\
GAT  &  &  &  \\
\bottomrule
\end{tabular}
\end{center}
Optional: compare \emph{random} vs \emph{scaffold} split on a subset.
\section*{6.\ Interpretability (Preview)}
GNNExplainer/IG visualizations for 2--3 molecules per dataset; brief notes on highlighted substructures.
\section*{7.\ Reproducibility \& Risks}
Seeds \& versions logged; config-driven runs; check class imbalance (Tox21) and small data (ESOL). Commands to reproduce are in \texttt{README.md}.
\end{document}
